Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-11 manuscript/manuscript.tex
Continue writing manuscript

Surprisingly both the linear and the exponential density tesseroid models needs the same values of distance-size ratio $D$ in order to assure a good accuracy.
Because the two functions are significantly different we can expect that these values of $D$ are good for a wide variety of density functions.\todo{no se si da para poner esto}

@@

The results can be seen in Figure \ref{fig:D-exp-power}.
Lower values of $b$ implies a more varying function.
We can see that for extremely varying functions the numerical model does not perform well: for a $b$=100m the difference is almost 100\%.

\todo{poner analisis con respecto al exponente cuando b=1000m}

@@

Secondly, lets assume the same density function from equation \ref{eq:density-discontinuous}, but now with an asymmetrical distribution: $R_c = (R_1 + R_2)/3$, and perform the same test.
We can see its results in Figure \ref{fig:D-discont-asym}: up to $D=10$ the difference between the numerical model and the analytical solution is greater than 10\%, what
lead us to conclude that the code does not reassembles the gravity fields for this case with good accuracy.

@@

In the light of these results we do not recommend using discontinuous densities functions. Instead, divide the tesseroid into several ones with specific homogeneous density or densityfunction for each one.

>>>>

Surprisingly both the linear and the exponential density tesseroid models needs the same values of distance-size ratio $D$ in order to assure a good accuracy.

@@

This tests were performed using both the thin and the thick spherical shell, and the results can be seen in Figure \ref{fig:D-exp-power}.
Taking into account that lower values of $b$ implies a more varying function, we can see that for extremely varying functions the numerical model does not perform well: for $b$=100m the difference is almost 100\% in the thin shell case, and the same happens with $b$=10km in the thick shell case.

On both cases, the model performs under the acceptable threshold for values of $b$ greater than the thickness of the shell, in other words, when the absolute value of the exponent in equation \ref{eq:density-exp} is lower than 1.
Although this sets a limitation to the model, the maximum acceptable variation is very far from real density distributions inside the Earth.
For example, if we take into account a tesseroid with 35km of thickness, a density of 2670kg/m$^3$ on its top surface and $b=35$km, then the density at its bottom will be approximately of 7000kg/m$^3$, very far from the values we can find at such depths.

@@

Secondly, lets assume the same density function from equation \ref{eq:density-discontinuous}, but now with an asymmetrical distribution: $R_c = (R_1 + R_2)/3$, and perform the same test.
We can see its results in Figure \ref{fig:D-discont-asym}: up to $D=10$ the difference between the numerical model and the analytical solution is greater than 10\%, what
leads us to conclude that the code does not reassembles the gravity fields for this case with good accuracy.

@@

In the light of these results we do not recommend using discontinuous densities functions. Instead, divide the tesseroid into several ones with specific homogeneous density or density function for each one.
